An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-16 ex3/paper/paper.tex
Small text changes

As finding adversarial flows is particularly difficult in our case, % for the reasons we discussed above,
we preferred methods  producing high-quality adversarial samples while not being as fast as other methods. We implemented the following \gls{aml} methods.

@@

$\delta \in \mathbb R$ determines the logit output of successful adversarial.
In the original publication $\delta=0$, which means that the network's decision for adversarial samples is just between attack and normal traffic. In the present context, we need to make sure that the classifier's prediction would actually be normal traffic, even though a certain level of noise will be added to \glspl{iat} due to the network between attacker and victim. Hence, we introduced $\delta=-0.2$, corresponding to a confidence of 55\% for the sample to be benign.

@@

The result is a number of adversarial samples and some that could not be made adversarial. If at least half of the samples are misclassified, we take 50\% of the samples, with those that required smaller modifications first. Of these samples, the distance of each adversarial sample to the original sample is taken and averaged. The resulting average distance is the \gls{ars}. The larger it is the better since then an adversary needs to modify the samples more to make them adversarial. If not more then half of the samples could be made adversarial, our metric is undefined since then apparently it is not possible for an adversary to reliably conduct adversarial attacks on the majority of samples. Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 % reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
 reasonable as outliers with very large distances are ignored and if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.
%we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.

\begin{figure}[h]
\includegraphics[width=\columnwidth]{../plots/ars_original.pdf}
\caption{Recall for each attack type and average modification per flow required by an adversary to make a flow appear benign for CIC-IDS-2017.}
\label{fig:recall_ars}
\end{figure}

>>>>

% Max: But FGSM is high-speed... So I removed this paragraph altogether
%As finding adversarial flows is particularly difficult in our case, % for the reasons we discussed above,
%we preferred methods  producing high-quality adversarial samples while not being as fast as other methods. We implemented the following \gls{aml} methods.

@@

$\delta \in \mathbb R$ is a parameter that determines how far an adversary wants to go over the decision boundary.
In the original publication $\delta=0$, which means that the network's decision for adversarial samples is just between attack and normal traffic. In the present context, we need to make sure that the classifier's prediction would actually be normal traffic, even though a certain level of noise will be added to \glspl{iat} due to the network between attacker and victim. Hence, we introduced $\delta=-0.2$, corresponding to a confidence of 55\% for the sample to be benign.

@@

The result is a number of adversarial samples and some that could not be made adversarial. If at least half of the samples are misclassified, we take 50\% of the samples, with those that required smaller modifications first. Of these samples, the distance of each adversarial sample to the original sample is taken and averaged. The resulting average distance is the \gls{ars}. The larger it is the better since then an adversary needs to modify the samples more to make them adversarial. If not more then half of the samples could be made adversarial, our metric is undefined since then apparently it is not possible for an adversary to reliably conduct adversarial attacks on the majority of samples. Then the ratio of samples that could be made adversarial ($<$50\%) can be useful metric to determine the exact extent of the adversarial threat. Setting the threshold for the \gls{ars} to 50\% is arbitrary, but
 % reasonable as this way the \gls{ars} approximates the median of the distances of all samples and, additionally, marks the distance where an adversarial attack is more likely to be successful than unsuccessful.
 reasonable as outliers with very large distances are ignored and if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''. 
%we think that it is reasonable since if an attacker can make the majority of samples adversarial, we think that its attack is ``successful''.

\begin{figure}[h]
\includegraphics[width=\columnwidth]{../plots/ars_original.pdf}
\caption{Recall for each attack type and average modification per flow required by an adversary to make a flow appear benign for CIC-IDS-2017.}
\todo{Show for which attack class not enough adversarial samples could be found.}
\label{fig:recall_ars}
\end{figure}
